---
title: "Cross Optimization"
author: "Freddy R. Drennan"
date: "November 25, 2017"
output:
  html_document:
    df_print: paged
  pdf_document:
    keep_tex: yes
    latex_engine: xelatex
---
---
name: "Freddy Drennan"
title: "Adwords Optimization"
date: "November 25, 2017"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    theme: cerulean
    highlight: haddock
    fig_align: center
---


<style>
body {
    background-color: #BCE6FF
}
</style>

<link rel="stylesheet" href="http://maxcdn.bootstrapcdn.com/font-awesome/4.3.0/css/font-awesome.min.css">

<div id="fb-root"></div>
<script>(function(d, s, id) {
  var js, fjs = d.getElementsByTagName(s)[0];
  if (d.getElementById(id)) return;
  js = d.createElement(s); js.id = id;
  js.src = "//connect.facebook.net/en_US/sdk.js#xfbml=1&version=v2.9&appId=1440881362667639";
  fjs.parentNode.insertBefore(js, fjs);
}(document, 'script', 'facebook-jssdk'));</script>

<div>

<!-- Footer -->
<header>
<!-- <div class="container"> -->
<div class="row">
<div class="col-lg-8 col-lg-offset-2 col-md-10 col-md-offset-1">
<ul class="list-inline text-center">
<li>
<a href="http://fdrennan.net">
<span class="fa-stack fa-lg">
<i class="fa fa-circle fa-stack-2x"></i>
<i class="fa fa-arrow-left fa-stack-1x fa-inverse"></i>
</span>
</a>
</li>
<li>
<a href="mailto:drennanfreddy@gmail.com?Subject=Hello">
<span class="fa-stack fa-lg">
<i class="fa fa-circle fa-stack-2x"></i>
<i class="fa fa-envelope fa-stack-1x fa-inverse"></i>
</span>
</a>
</li>
<li>
<a href="https://www.linkedin.com/in/freddy-drennan-4a8b79aa">
<span class="fa-stack fa-lg">
<i class="fa fa-circle fa-stack-2x"></i>
<i class="fa fa-linkedin fa-stack-1x fa-inverse"></i>
</span>
</a>
</li>
<li>
<a href="http://facebook.com/freddy.drennan">
<span class="fa-stack fa-lg">
<i class="fa fa-circle fa-stack-2x"></i>
<i class="fa fa-facebook fa-stack-1x fa-inverse"></i>
</span>
</a>
</li> 
<li>
<a href="http://kaggle.com/fdrennan">
<span class="fa-stack fa-lg">
<i class="fa fa-circle fa-stack-2x"></i>
<i class="fa fa-area-chart fa-stack-1x fa-inverse"></i>
</span>
</a>
</li> 
<li>
<a href="https://github.com/fdrennan">
<span class="fa-stack fa-lg">
<i class="fa fa-circle fa-stack-2x"></i>
<i class="fa fa-github fa-stack-1x fa-inverse"></i>
</span>
</a>
</li>
</ul>
</div>
</div>
</div>
</header>

################################################




Loading the necessary packages
```{r, warning = FALSE, message = FALSE}
library(tidyverse)
library(lpSolve)
```



Starting Data: 
```{r}
# Revenue variables

initial_data <- 
  tibble(
    origin  = c(
      'search', 
      'display', 
      'youtube', 
      'gmail'
    ),
    revenue = c(
      225776, 
      99292, 
      4120, 
      2472
    ),
    cost    = c(
      8827,
      5172,
      833,
      423
    )
  ) %>% 
    mutate(
      roi = (revenue - cost) / cost
    )
```

Constraints:

* Total budget for all digital ads will not exceed 15000
* Minimum: 3000 should be spent on Display ads
* Minimum: 400  should be spent on Social YouTube
* Display Ads and YouTube ads must exceed 60% of total budget
* YouTube Ads should not cost more than Gmail Ads. 
* Minimum 1500 franchise application form. 


+ $x_1$ = Search Ads
+ $x_2$ = Display Ads
+ $x_3$ = YouTube Ads
+ $x_4$ = Gmail Ads

We want to increase revenue, so the objective function should be maximized regarding the constraints. 

```{r}
A <-  
  matrix(
    c(
     1,    1,    1,    1,
     0,    1,    0,    0,
     0,    0,    1,    0,
  -0.6,  0.4,  0.4, -0.6,
     0,    0,   -1,    1, 
   .13,  .09,  .02,  .03
    ),
  ncol = 4,
  byrow = TRUE
  )

b <- 
  c(
    15000,
    3000,
    400,
    0,
    0,
    1500
  )

dir <- 
c(
  "<=",
  ">=",
  ">=",
  ">=",
  ">=",
  ">="
)

obj <- 
  c(
    initial_data$roi
  )
```

$$
\text{max}\:\:(x_1 + x_2 + x_3 + x_4)
$$

```{r}
cbind(A, dir, b) %>% 
  noquote() 
```

```{r}
s = lp(
  "max", # Maximize or minimize function
  obj,   # Objective function to maximize
  A,     # constraint matrix
  dir,   # direction of equalities
  b      # b vector of constraint coeffs
)

solution <- 
  s$solution

names(solution) <- 
  initial_data %>% 
  pull(origin) %>% 
  paste0("Budget-", .)

solution
```


```{r}
A %*% solution %>% 
  round(2)
```


Cleaning up data to display
```{r}

sol_tib <- 
  tibble(
  x_1 = rep(NA, 6),
  x_2 = rep(NA, 6),
  x_3 = rep(NA, 6),
  x_4 = rep(NA, 6)
)

for(i in 1:nrow(A)) {
  solz <- 
    paste0(A[i,], " * ", solution, " + ") %>% 
    noquote 
  
  sol_tib[i, 1:4] <- 
    solz
}

sol_tib <-
  sol_tib %>% 
  mutate(
    equals            = rep("=", 6),
    sol               = A%*%solution %>% round(2),
    x_4               = sub("\\+", "", x_4) %>% str_trim,
    'constraints==>'  = rep("...", 6),
    dir               = dir,
    b                 = b
  ) %>% 
  as.data.frame

  
sol_tib
```
























##############################################
<div>

<!-- Footer -->
<header>
<!-- <div class="container"> -->
<div class="row">
<div class="col-lg-8 col-lg-offset-2 col-md-10 col-md-offset-1">
<ul class="list-inline text-center">
<li>
<a href="http://fdrennan.net">
<span class="fa-stack fa-lg">
<i class="fa fa-circle fa-stack-2x"></i>
<i class="fa fa-arrow-left fa-stack-1x fa-inverse"></i>
</span>
</a>
</li>
<li>
<a href="mailto:drennanfreddy@gmail.com?Subject=Hello">
<span class="fa-stack fa-lg">
<i class="fa fa-circle fa-stack-2x"></i>
<i class="fa fa-envelope fa-stack-1x fa-inverse"></i>
</span>
</a>
</li>
<li>
<a href="https://www.linkedin.com/in/freddy-drennan-4a8b79aa">
<span class="fa-stack fa-lg">
<i class="fa fa-circle fa-stack-2x"></i>
<i class="fa fa-linkedin fa-stack-1x fa-inverse"></i>
</span>
</a>
</li>
<li>
<a href="http://facebook.com/freddy.drennan">
<span class="fa-stack fa-lg">
<i class="fa fa-circle fa-stack-2x"></i>
<i class="fa fa-facebook fa-stack-1x fa-inverse"></i>
</span>
</a>
</li> 
<li>
<a href="http://kaggle.com/fdrennan">
<span class="fa-stack fa-lg">
<i class="fa fa-circle fa-stack-2x"></i>
<i class="fa fa-area-chart fa-stack-1x fa-inverse"></i>
</span>
</a>
</li> 
<li>
<a href="https://github.com/fdrennan">
<span class="fa-stack fa-lg">
<i class="fa fa-circle fa-stack-2x"></i>
<i class="fa fa-github fa-stack-1x fa-inverse"></i>
</span>
</a>
</li>
</ul>
</div>
</div>
</div>
</header>

<div class="fb-comments" data-href="http://fdrennan.net/pages/pages2/Cross_Optimization.html" data-numposts="5"></div>


